Quasi-likelihood models

### 2021-10-11 text/Rmd/quasi-likelihood/index.Rmd
Updated glm-deviance.Rmd

The generalized linear model for any distribution in the exponential family can be described in terms of a link function and a variance function.

@@

>>>>

A distribution is said to be in the exponential family

$ln f(y, \theta)=d(\theta)e(y)+g(\theta)+h(y)$

but sometimes this is rewritten in the form

$ln f(y, \theta)=\frac{\theta y+b(\theta)}{a(\phi)}+c(y, \phi)$

where $\phi$ is a dispersion or scale parameter. This is called the canonical form. There are names for these parameters and functions.

+ $\theta$ is the natural parameter,
+ $\phi$ is the dispersion parameter,
+ $a(\ ) is the variance function, and
+ $g(\ ) = b'(\ )^{-1} is the link function.

If you also define

$\mu=E[Y]$

then the link function, g, and its inverse, b, define how the regression model works.

@@

$ln(f(y, \lambda) = ln(\frac{\lambda^y e^{-\lambda}}{y!})=\lambda ln(\lambda)-\lambda-ln(y!)$

To write this in the canonical form, you need to define the natural parameter as

$\theta=ln(\lambda)$

and

$a(\phi)=1$

The link function is
